The \dealii{} Library, Version 9.3

### 2021-05-24 9.3/paper.tex
Add some relevant minor-change topics

The major changes of this release are:
%
\begin{itemize}
  \item TODO.
\end{itemize}
%
These major changes are discussed in detail in Section~\ref{sec:major}. There
are a number of other noteworthy changes in the current \dealii{} release
that we briefly outline in the remainder of this section:
%
\begin{itemize}
  \item globally unique cell IDs: TODO
\end{itemize}
%
The changelog lists more than 240 other
features and bugfixes.

>>>>

The major changes of this release are:
%
\begin{itemize}
  \item TODO.
\end{itemize}
%
These major changes are discussed in detail in Section~\ref{sec:major}. There
are a number of other noteworthy changes in the current \dealii{} release
that we briefly outline in the remainder of this section:
%
\begin{itemize}
  \item globally unique cell IDs: TODO
  \item In addition to the macro \texttt{DEAL\_II\_DEPRECATED}, we have introduced
  the \texttt{DEAL\_II\_DEPRECATED\_EARLY} macro, which indicates that a feature will be
  deprecated in the next release. In contrast to the first macro, it will only give
  warnings if \dealii{} has been configured with \texttt{-D DEAL\_II\_EARLY\_DEPRECATIONS=ON}.
  \item After each update of the master branch of \dealii{}, we build a new Docker image
  with all features enabled. It is
  accessible on \texttt{Docker Hub} via \texttt{dealii/dealii:master-focal}. This image is
  particular useful when used in the contiguous-integration processes of user codes.
\end{itemize}
%
The changelog lists more than 240 other
features and bugfixes.
